Fast and optimal centroiding of faint stars

### 2014-12-31 ms/figure.tex
Update figure.tex

In this experiment, after finding the centroiding error for each method,
we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}], [\ref{5}]. All methods deliver results with RMSE larger for fainter stars.
In case of 3$\times$3 polynomial centroiding [\ref{1}], RMSE becomes very large as we move towards the fainter stars in our simulation. Moreover, we observe a kink in the plot of RMSE against SNR. For stars with larger $\gamma$, this kink moves toward higher values of SNR. As it can be seen in figure [\ref{1}], centroid estimate from the polynomial method do not even get close to saturating the CRLB. By increasing $\gamma$, RMSE moves further away from the CRLB.

However, RMSE from the modified centroiding method [\ref{2}], and RMSE from the quartic approximation [\ref{3}] method are very close to the CRLB. As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer to the CRLB. This implies that as stars get undersampled, the performance of these two models get slightly worse. But if we increase $\gamma$ to 4 and 5.6 pixels, RMSE gets farther from the CRLB. This is quite predictable since these two models only use the information contained in a 3$\times$ 3 patch. It is also important to note that the rate at which the RMSE from these two method drops eventually becomes smaller than the constant rate at which the CRLB decreases with increaing SNR.

As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{4}] lies on the CRLB. Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB. As it can be seen in figure [\ref{5}], even the centroid estimates found by fitting a wrong PSF model (Gaussian PSF) to the simulated stars saturate the CRLB.

\subsection{Experiment 2}
In this experiment, after finding the centroiding error for each method, we compute the RMSE in bins of $\gamma$ in order to compare it to the CRLB. 
Behavior of error as a function of $\gamma$ for different values of SNR, is shown in figures [\ref{6}], [\ref{7}], and [\ref{8}], [\ref{9}], and [\ref{10}].

The centroid estimates obtained from the 3$\times$3 polynomial method [\ref{6}] result in RMSE much larger than the CRLB in all ranges of FWHM and for all four values of SNR in this experiment. In the case of extremely faint stars (SNR = 5), the polynomial method is not able to deliver any reliable estimate, and completely fails.

The 3$\times$3 modified polynomial method [\ref{7}], and the 3$\times$3 quartic approximation [\ref{8}] result in RMSE very close to the CRLB. For al four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels, RMSE gets slightly closer to the CRLB since these two models start to work slightly worse as we decrease $\gamma$ and move towards undersampled stars. After approximately 3 pixels, increasing $\gamma$ deviate RMSE of these methods from the CRLB. This is inherent characteristic of all 
3$\times$3 methos. Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) closer to the CRLB.

Again The RMSE from centroiding by fitting the exact PSF model as a function of FWHM perfectly lies on the CRLB [\ref{9}]. Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB. Once again, we observe that the centroid estimates found by fitting a Gaussian PSF to the simulated stars also saturate the CRLB in all ranges of $\gamma$ [\ref{10}].

>>>>

In this experiment, after finding the centroiding error for each method,
we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}],
[\ref{3}], [\ref{4}], [\ref{5}], [\ref{6}]. All methods deliver results
with RMSE larger for fainter stars.
In case of 3$\times$3 polynomial centroiding [\ref{1}], RMSE becomes
very large as we move towards the fainter stars in our simulation.
Moreover, we observe a kink in the plot of RMSE against SNR.
For stars with larger $\gamma$, this kink moves toward higher values of SNR.
As it can be seen in figure [\ref{1}], centroid estimate from the polynomial
method do not even get close to saturating the CRLB. By increasing $\gamma$,
RMSE moves further away from the CRLB.

However, RMSE from the modified centroiding method [\ref{2}],
and RMSE from the quartic approximation [\ref{3}] method are very
close to the CRLB except at the very small values of SNR (SNR $<$ 10).
As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer
to the CRLB. This implies that as stars get undersampled, the performance
of these two models get slightly worse. But if we increase $\gamma$ to
4 and 5.6 pixels, RMSE gets farther from the CRLB.
This effect is quite predictable since these two models only use the
information contained in a 3$\times$ 3 patch. It is also important to
note that the rate at which the RMSE from these two method drops
eventually becomes smaller than the constant rate at which the CRLB
decreases with increaing SNR. Also the results from 7$\times$7 weighted moment
method [\ref{4}] suggest that this method does worse than the qurtic approximation, and
the modified polynomial method, and at low values of SNR the centroiding RMSE from
this method moves significantly away from the CRLB.

As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{5}]
lies on the CRLB except at values of SNR below 10 where the RMSE gets slightly pulled away
from the CRLB because of the presence of a few outliers.
Thus, centroid estimates from fitting the exact PSF model always
saturate the CRLB. As it can be seen in figure [\ref{6}],
even the centroid estimates found by fitting a wrong PSF model (Gaussian PSF)
to the simulated stars saturate the CRLB.

\subsection{Experiment 2}
In this experiment, after finding the centroiding error for each method, we
compute the RMSE in bins of $\gamma$ in order to compare it to the CRLB. 
Behavior of error as a function of $\gamma$ for different values of SNR,
is shown in figures [\ref{7}], [\ref{8}], and [\ref{9}], [\ref{10}], [\ref{11}], and [\ref{12}].

The centroid estimates obtained from the 3$\times$3 polynomial method [\ref{7}]
result in RMSE much larger than the CRLB in all ranges of FWHM and for all four
values of SNR in this experiment. In the case of extremely faint stars (SNR = 5),
the polynomial method is not able to deliver any reliable estimate, and completely fails.

The 3$\times$3 modified polynomial method [\ref{8}], and the 3$\times$3
quartic approximation [\ref{9}] result in RMSE very close to the CRLB.
For al four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels,
RMSE gets slightly closer to the CRLB since these two models start to work
slightly worse as we decrease $\gamma$ and move towards undersampled stars.
After approximately 3 pixels, increasing $\gamma$ deviate RMSE of these methods from the CRLB.
This is inherent characteristic of all 3$\times$3 methos. 
Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) get
closer to the CRLB. Also we observe that in the case of 7$\times$7 weighted moment 
centroiding, deviation of the centroiding RMSE from the CRLB is significantly higher
than those of 3$\times$3 quartic approximation, and 3$\times$3 modified polynomial.

Again The RMSE from centroiding by fitting the exact PSF model as a function of FWHM
perfectly lies on the CRLB [\ref{11}] except at SNR = 5 where the RMSE slightly deviates
from the CRLB due tp the presence of outliers. Thus, centroid estimates from fitting
the exact PSF model always saturate the CRLB. Once again, we observe that the centroid
estimates found by fitting a Gaussian PSF to the simulated stars also saturate
-- except in the case of SNR = 5-- the CRLB in all ranges of $\gamma$ [\ref{12}].
